# The Physical Space

## Where

The Linguistics Computation Lab (LinCoLab) is located in the basement of [Breckenridge Hall](https://efacts.uky.edu/Details?id=breckinridge_hall), room 10.

```{r}
#| echo: false

library(leaflet)
leaflet(
  height = 50,
  width = 100,
  #options = leafletOptions(maxZoom = 30)
) |> 
  addTiles() |> 
  addMarkers(lat = 38.03513, lng = -84.50511, popup = "The LinCoLab") |> 
  addMarkers(lat = 38.03859, lng = -84.5043, popup = "The Linguistics Department")
```

## Access

The exterior doors of Breckenridge Hall are key-locked. Outside of normal business hours, they may be locked. Only the director and the Linguistics Department manager have keys to the exterior doors.

The interior door to the lab is also key-locked. There are a limited number of keys that can be signed out by members from the Linguistics Department manager.

**The last person to leave the lab is responsible for locking it!**

## Taking Care of the Space

### Food and drink

It is ok to bring food or drink to the lab, but you must pack out whatever you pack in. We can't throw away food waste inside the lab. We also can't *store* food in the lab.

**Please try to clean up any spills as soon as they happen.**

### The whiteboards

It is ok to write on the whiteboards, but anything written on them *might* be erased at any time.

### Decorations

Please consult with the lab director before adding or subtracting any lab decorations.

### Windows

It is ok to open the windows while you are in the lab.

**If you are the last person to leave the lab, you must close and lock them.**

### Desks, and chairs

All space in the lab is common space.

## Facilities

Directly across the hall from the lab entrance is an all gender bathroom.

## What's around

The closest place to get a cup of coffee and snack is Einstein Bagels in the Chemistry-Physics building. After that is the Starbucks in the William T Young Library.

```{r}
#| echo: false
leaflet(
  height = 60,
  width = 100,
  #options = leafletOptions(maxZoom = 30)
) |> 
  addTiles() |> 
  addMarkers(lat = 38.03513, lng = -84.50511, popup = "The LinCoLab") |> 
  addMarkers(lat =38.03518, lng= -84.50416, popup = "Einstein Bagels") |> 
  addMarkers(lat = 38.03259, lng = -84.50135, popup = "Starbucks")
```
